Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/tech_report/overview.tex
Edits to overview.

We turn to our analytical model to compute the \emph{cost} of the iterative program. Assume
cost $\beta$ for a local MPC operation (e.g., ADD in Arithmetic sharing) and cost $\alpha$ for a remote
MPC operation (e.g., MUX, CMP, etc.). Assuming that ADD is $\alpha$ and SUM, CMP and MUX are $\beta$, 
the MPC Source in Listing~\ref{tab:source_and_MPC_source_and_optimized_MPC_source}(b) gives 
rise to an iterative schedule with cost $ND(2\alpha+\beta) + N(3\alpha$).

>>>>

We turn to our analytical model to compute the \emph{cost} of the iterative program. Assume
cost $\beta$ for a local MPC operation (e.g., ADD in Arithmetic sharing) and cost $\alpha$ for a remote
MPC operation (e.g., MUX, CMP, etc.). Assuming that ADD is $\beta$ and SUM, CMP and MUX are $\alpha$, 
the MPC Source in Listing~\ref{tab:source_and_MPC_source_and_optimized_MPC_source}(b) gives 
rise to an iterative schedule with cost $ND(2\alpha+\beta) + N(3\alpha$).
